### 2023-09-26 main.tex
check

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present. As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}. \\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space $\Omega=\bigtimes_{x=1}^{L} \Omega_{x}$ and its generator reads

@@

@@

This can be represented by the following diagram 

@@

@@

As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$. Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 

@@

where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. 

@@

%\subsection{Bethe ansatz solution}
%Describe eigenvalues of $T_0$ following 
%\cite{belliard2} 
\subsection{A sequence of similarity transformation}
In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$
 Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one $H_{0}$ as 
As a consequence for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
Moreover, using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
\section{Extensions for the non-integrable chain}
In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
The aim of this section is studying some extension of the analysis previously done when integrability property is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
	%\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average density evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is proved. Subsection \ref{Subsection-RD}

@@

The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace} and its generator reads

@@

In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n_{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters. 

@@

The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{dualStateSpace}. Its generator reads

@@

	d_{x}(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}

@@

	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&

@@

	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{1}^{k}}\prod_{x=2}^{N}d_{x}(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}

>>>>

In this subsection we specialize the results of Subsection \ref{statementDualitySubsection} to a chain of length $L$, where two reservoirs are attached to sites $1$ and $L$. Each site can still host $\nu\geq 1$ particles, chosen among the $N$ types. Now the dual graph is still a chain, but where two extra-sites $0$ (connected to $1$) and $L+1$ (connected to $L$) are present. As already pointed out the dual process eventually voids the graph by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites ($0$ and $L+1$) and replacing them by types $N$. This property allows to characterize the steady state non-equilibrium distribution (assuming that it is unique) by the probability that dual particles are absorbed in the extra-sites, then called \textit{absorption probabilities}. \\The process $\left(\bm{n}(t)\right)_{t\geq0}$ is defined on the space
 \begin{equation}\label{stateSpace-Chain}
 	\Omega=\bigtimes_{x=1}^{L} \Omega_{x}
 \end{equation} and its generator reads

@@

\begin{equation}\label{stateSpaceDUAL-Chain}	

@@

This can be represented by the diagram 

@@

Namely, the following equation holds true

@@

As a consequence, using this sequence of transformations we can find all the eigenvectors of $H$ from the ones of $H_{0}$
Moreover, this allows to retrieve the steady state of $H$, by applying the sequence of transformation to the vacuum state of $H_{0}$, i.e. a state where all the sites are empty. This last transformation $W$ is non-local and to be constructed requires a joint work of perturbation theory and integrability, via the Quantum Inverse Scattering Method (QISM). 

@@

where $\Delta_{i}=(\alpha_{i}-\beta_{i})$ for every $i\in\{1,\ldots,N-1\}$. \\
As a consequence, the steady state of the original process $H$ reads

@@

%\subsection{Bethe ansatz solution}
%Describe eigenvalues of $T_0$ following 
%\cite{belliard2} 
\subsection{A sequence of similarity transformation}
In Subsection \ref{subsection-exact} and \ref{SectionNonLocalTrasformation} we have found three similarity transformations, namely $S_{1}$, $S_{2}$ and $W$ between operators $H$, $H^{'},H^{''}$ and $H_{0}$
\begin{equation}
	H\;\xleftrightarrow{S_{1}}\;H^{'}\;\xleftrightarrow{S_{2}}\;H^{''}\xleftrightarrow{W}\;H_{0}
\end{equation} 
 Using them simultaneously one can map the non-equilibrium Hamiltonian $H$ onto the equilibrium one $H_{0}$ as 
\begin{equation}
	H_{0}=W^{-1}\,S_{2}\,S_{1}\,H\,S_{1}^{-1}\,S_{2}^{-1}\,W
\end{equation}
As a consequence for a fixed configuration $\bm{m}$, the non-equilibrium eigenvectors can be mapped to the equilibrium ones as
\begin{equation}
	|\Psi_{\bm{m}}\rangle=S_{1}^{-1}S_{2}^{-1}W|\Psi_{\bm{m}}^{0}\rangle
\end{equation}
Moreover, using \eqref{SteadyState-W-Good} the steady state of $H$ defined in \eqref{definition-SteadyStateH} can be obtained from the vacuum state $|\Psi_{0}^{0}\rangle$ defined in \eqref{Vacuum-state} as
\begin{align}
	|\Psi\rangle=&\text{exp}\left(-\sum_{x=1}^{L}\sum_{a=1}^{N-1}e_{Na}^{x}\right)\text{exp}\left(\sum_{x=1}^{L}\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)\nonumber\\&
	\sum_{k_{1}=0}^{L}\ldots\sum_{k_{N-1}}^{L}\mathbbm{1}_{\{k_{1}+\ldots+k_{N-1}\leq L\}}\frac{(\alpha_{1}-\beta_{1})^{k_{1}}\cdots (\alpha_{N-1}-\beta_{N-1})^{k_{N-1}}}{k_{1}!\cdots k_{N-1}!}\nonumber\\&
	\left(\frac{B_{1}^{2L-1}}{2^{k_{1}}}\right)^{k_{1}}\cdots\left( \frac{B_{N-1}^{2L-1}}{2^{k_{N-1}}}\right)^{k_{N-1}}\frac{\Gamma\left(e_{NN}^{tot}+2-(k_{1}+\ldots+k_{N-1})\right)}{\Gamma\left(e_{NN}^{tot}+2\right)}|\Psi_{0}^{0}\rangle
\end{align}
Observe that, while $S_{1}$ and $S_{2}$ are local, $W$ is not. 
\end{comment}
\section{Extensions for the non-integrable chain}
In Sections \ref{sectionIntegrabiliy} and \ref{Section-Mapping} we have shown that, on the geometry of a chain and with hard-core interaction the model is exactly solvable thanks to integrability.  
The aim of this section is studying some property of the process when integrability is lost. We fix $\nu\geq 1$ and, for the sake of simplicity, we keep the geometry of a chain. We provide the following extensions: 
\begin{enumerate}
	%\item \textit{Arbitrary correlations}: exploiting duality, the steady state correlations can be expressed in terms of absorption probabilities of the dual particles. These probability are hard to find in this partial exclusion situation, however correlation can be formally written. Subsection \ref{Subsection-ss-nonI}.
	\item \textit{Instantaneous thermalization}: starting from the multi-species stirring dynamics, we define the thermalized process, where particle are redistribute in each bond with a measure that is the reversible one conditioned to the conservation of the number of particles on this bond. Also for this thermalized process we prove duality. Subsection \ref{Subsection-Thermalized}.
	\item \textit{Reaction-diffusion process}: a further dynamics is added. Particle can now change type. The model is carefully constructed with the goal of having the average densities evolving as a system of $N-1$ coupled difference-differential equation, providing a generalization of the model studied in \cite{casini2022uphill}. Duality for the boundary driven process is also proved. Subsection \ref{Subsection-RD}
\end{enumerate}

@@

The thermalized multi-species stirring process is defined on the configuration space $\Omega$ introduced in \eqref{stateSpace-Chain} and its generator reads

@@

In the thermalized bulk generator particles on a bond $x$ and $x+1$ are redistribute according to the measure $\nu_{TH}(\bm{r}|\bm{\epsilon})$, while in the thermalized boundary generators the configuration at site $1$ (and $L$) $n^{1}$ is replaced by $\bm{r}$, according to a rate depending on the reservoirs parameters. 

@@

The thermalized dual process $(\bm{\xi}(t))_{t\geq 0}$ is defined on the enlarged configuration space $\widetilde{\Omega}$ introduced in \eqref{stateSpaceDUAL-Chain}. Its generator reads

@@

	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}

@@

	\left.\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{a}^{R})^{\xi_{d}^{L+1}}-D(\bm{n},\bm{\xi})\right\}

@@

	&\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}\left\{\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{|\alpha|}\right)^{\xi_{a}^{0}}\frac{\left(\nu-\sum_{c=1}^{N-1}\xi_{c}^{1}\right)!}{\nu!}\prod_{b=1}^{N-1}\frac{r_{b}!}{(r_{b}-\xi^{1}_{b})!}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}\right\}\nonumber\\&	\frac{\nu!}{r_{1}!\cdots r_{N}!}\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{\alpha_{N}}\right)^{r_{k}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu-\xi_{\ell}^{1}+\xi_{\ell}^{1}-r_{\ell}+r_{\ell}}\prod_{\ell=1}^{N-1}\left(\frac{\alpha_{\ell}}{|\alpha|}\right)^{\xi_{1}^{1}+\xi_{1}^{2}-\xi_{2}^{1}+\xi_{2}^{1}}\nonumber\\=&
	\prod_{k=1}^{N-1}\left(\frac{\alpha_{k}}{|\alpha|}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\sum_{r_{1}=0}^{\nu}\ldots\sum_{r_{N}=0}^{\nu}\mathbbm{1}_{\{r_{1}+\ldots+r_{N}=\nu\}}	\frac{\left(\nu-\xi_{1}^{1}-\ldots-\xi_{N-1}^{1}\right)!}{(r_{1}-\xi_{1}^{1})!\cdots(r_{N-1}-\xi_{N-1}^{1})!(\nu-r_{1}-\ldots-r_{N-1})!}\nonumber\\&

@@

	\prod_{k=1}^{N-1}\left(\rho_{k}^{L}\right)^{\xi_{k}^{0}+\xi_{k}^{1}}\prod_{x=2}^{L}d(n^{x},\xi^{x})\prod_{d=1}^{N-1}(\rho_{d}^{R})^{\xi_{d}^{L+1}}
